Time Series Analysis of Chaotic Dynamical Systems with Recurrent Neural Networks

### 2019-04-18 doc/paper/paper.tex

Most well performing models couldn't predict past one Lyapunov constant. From
the graphs, we can see that most models deviated once reaching the
intersection of the butterfly wings.

@@

%% CONCLUSION %%%
\section{Conclusion}

>>>>

Most well performing models could predict around one Lyapunov time constant. 
From the graphs, we can see that most models deviated once reaching the
intersection of the butterfly wings.

@@

Generating data for the 3 body problem was more difficult since we have to becareful that the trajectory doesn't diverge or collide with the other bodies.

When the bodies collide, then the problem becomes a stiff problem and the
trajectory might be inaccurate, and when the bodies diverge, the trajectory
becomes a simple spiral without chaotic properties. Initial conditions which
don't run into these issues are usually orbital. Such solutions exist
\cite{frnkacase}, and \texttt{echonn} finds them by randomly generating initial
conditions, and testing for the conditions. Orbital patterns happen frequently
enough that they can be found easily with this method.

The case I analyze, the initial conditions were found to be 
$(x, x', y, y')_{t=0} = (0.79563053, 0, 0, 0.96833226)$
with a largest Lyapunov Exponent of 0.1759. This case is much different than 
the other systems since it doesn't have strong chaotic properties. This can
be seen in the orbital pattern which seems quasi-periodic, and it might be. 
In light of this, it's also very possible that the measured chaotic properties
are solely due to error in the numerical calculation. However, the orbiting
doesn't repeat exactly, so there are still small complexities for the ESN
to pick up on. 
%% CONCLUSION %%%
\section{Conclusion}
